% !TEX root = _main.tex
\section{Introduction}
Understanding how immigration and immigration policy affect U.S. labor markets has long been a central question for economists. Existing work predominantly focuses on how immigration affects U.S. firms and local labor markets, with a particular emphasis on native workers. A key element, however, that is overlooked by focusing only on aggregate effects, is how immigrant workers themselves are affected by immigration policy. Understanding how individual foreign workers are impacted by obtaining U.S. work authorization, what their counterfactual outcomes in the absence of the authorization might have been, and how these effects vary across different types of workers and over time, is crucial for understanding the efficiency and distributional consequences of immigration policy. Furthermore, accurately understanding how firms and workers currently utilize the immigration system, an important consideration for crafting effective immigration policy, requires tracking individual workers through the immigration process.

% Option 1: Over the last x years, demand for U.S. work permits has skyrocketed (stat). While many prospective immigrants cite beliefs about x, y, z, quantitative evidence on the individual-level effects of obtaining a U.S. worker visa is scarce. 

% Option 2: Immigration is important.. lot of econ literature studies effects on U.S. labor market... Missing element is impact on individual foreign workers -- global efficiency/innovation, imm policy/demand, etc.

Estimating the individual-level effects of obtaining a work permit, however, is difficult for two reasons: first, because obtaining a work permit is generally not exogenous to worker outcomes, and second, because individual-level data on immigration status and visa receipt, when made available, are generally deidentified and therefore difficult to link to data on labor market outcomes. 
In this project, I overcome these two hurdles by using individual application data from the H-1B visa lottery. The H-1B visa is an employer-sponsored visa intended to help firms fill gaps in the domestic labor force by hiring highly-skilled foreign workers for specialized roles.  
For many years, demand for H-1B visas has far exceeded the annual cap of 85,000 visas, leading to a lottery system for visa allocation that creates random variation in visa receipt among applicants. Using probabilistic linkage methods, I link a subset of deidentified H-1B lottery applications between 2020 and 2023 to individual work histories from LinkedIn data provided by Revelio Labs. I am, to my knowledge, the first to construct such a panel of H-1B lottery applicants linked to individual-level outcomes.

Considerable past research has studied the effects of H-1B visa access on the U.S. labor market \citet{boundetal2017, doranetal2022, mahajanetal2024}. This literature, however, has entirely focused on firm and local labor market outcomes, and largely covers lotteries prior to 2010. Two key institutional details enable me to study individual-level effects for more recent years of the lottery. First, while U.S. Citizenship and Immigration Services (USCIS) keeps administrative records on H-1B lottery winners in all years, it was only starting with the 2020 lottery that USCIS began to also keep records of lottery \textit{losers}. Thus, while most prior papers use a proxy for lottery applications to identify firm-level effects, the availability of data on the full universe of applicants allows me to directly observe both individual winners and losers. 

The second key insight is that the composition of H-1B applicants has changed over time. The administrative data I use is deidentified and contains detailed information about the sponsoring employer but only basic demographic information about the applicant themselves. 
The canonical view of an H-1B applicant is that of a worker from abroad who is hired by the sponsoring firm if and only if they win the lottery and obtain an H-1B visa. In this setting, it is essentially impossible to identify lottery losers: armed with only basic demographics and no employer information, the set of possible matches would be overwhelmingly large. 

% Over the last 15 years, however, increased usage of Optional Practical Training (OPT) by international students has changed how many companies use the H-1B visa. OPT is a temporary work authorization that allows students on F-1 visas to work in the United States immediately following graduation. In the 2024 H-1B lottery, over x\% of applicants had previously been on F-1 visas, and thus eligible to work under OPT prior to the H-1B lottery. 

In reality, however, a large share of modern H-1B applicants are already working in the United States before the lottery, most commonly under F-1 Optional Practical Training (OPT).\footnote{The number of F-1 students obtaining H-1B visas grew from 29,000 in FY2008 to 52,000 in FY2024 .} For this group, the sponsoring firm often employs the worker before it enters the lottery. By subsetting to international students who were \textit{already working for the sponsoring firm at the time of the lottery}, I can reduce the candidate pool from the entire LinkedIn universe to the much smaller set of individuals working at the sponsoring firm.
Furthermore, because I select the candidate pool based only on information on employment prior to the lottery, this OPT subsample is not subject to selection bias based on the lottery outcome.

Using these two insights, I am able to construct a linked applicant panel that includes both lottery winners and losers who had already been working for the sponsoring firm before the lottery. I then estimate the causal effect of winning the H-1B lottery on the individual worker by comparing outcomes for winners and losers in this linked sample.\footnote{I condition only on Advanced Degree Exemption (ADE) status, an indicator for whether an individual received an advanced degree (Master's or higher) from a U.S. institution. ADE applicants face a different lottery process and generally experience higher rates of success in the H-1B lottery.} Identification relies on the standard lottery assumption that, conditional on ADE status, selection is independent of applicant potential outcomes. In my main specification, I also include firm-by-lottery-year fixed effects, which compare winners and losers within the same sponsoring firm and lottery year.

I find that winning the H-1B lottery increases individuals' probability of remaining in the United States by 0.53 percentage points (0.6\%\sym{***}) and of remaining at the sponsoring employer by 0.44 percentage points (0.8\%\sym{**}) two years after the lottery. Accordingly, winners are less likely to be observed in their home country (0.14 percentage points, 6.4\%\sym{*}) and puzzlingly more likely to have enrolled in new education (0.42 percentage points, 1.2\%\sym{*}), although these results flip in other samples. These effects are statistically significant but small in magnitude.

One likely reason for these small estimates is that my  probabilistic linkage inevitably introduces measurement error, which attenuates treatment effects toward zero. I address this issue in several ways by using alternate samples of higher quality matches. I find that the estimated effects are larger in those samples, consistent with the idea that measurement error is attenuating the estimates in the full sample, but the effects remain small even in the highest-quality subsamples.

Why might we see such small effects of the H-1B lottery on individual outcomes? The main consideration is that by design, I am subsetting to individuals who are already working for the sponsoring firm before the lottery, and therefore have an active work permit at the time of the lottery. If it is indeed the case that I am capturing individuals on OPT, as intended, I should see that the estimated effect of winning the lottery is larger for individuals who are closer to the end of their OPT runway. I find suggestive evidence that the effects of winning the lottery are stronger for applicants who are either one or three years post-graduation (the years when regular OPT and the STEM OPT extension respectively expire). This pattern suggests that the small average effects may reflect the fact that many lottery losers are able to remain at the firm or in the United States through OPT for some time after the lottery, and therefore the main effect of lottery loss may be to weaken firm attachment, reduce employment stability, or accelerate return migration only at the margin.

These findings speak to several literatures. First, to my knowledge I am the first to estimate the causal effect of winning the H-1B lottery on an individual worker. An extensive body of work studies the aggregate and firm-level consequences of the H-1B visa, including the impacts on native employment and wages \citep{kerr_kerr_lincoln_2015, peri_shih_sparber_2015_lottery,doranetal2022,mahajanetal2024} and innovation and productivity \citep{kerrlincoln2010,peri_shih_sparber_2015_stem,dimmock_huang_weisbenner_2022, mayda_etal_2023}. 
A related line of work emphasizes how immigration rules can shape firms' outside options and the global geography of work, for example by inducing offshoring or affecting destination choices outside the United States \citep{ khannamorales2017, brinattiguo2023,glennon2024}. Another literature highlights that temporary work visas may generate employer-specific rents by restricting worker mobility and tying legal status to the sponsoring employer \citep{kimpei2022}. This paper complements those studies by shifting the unit of analysis from the firm to the worker. In particular, I am able to capture the responses of individual lottery losers, who are generally not visible in firm-level analyses. Additionally, by extending analysis to more recent years of the lottery, I capture how the effects of the lottery have evolved over time as the composition of applicants has changed and as the institutional environment has evolved.

Second, I make a methodological contribution by developing a probabilistic linkage procedure tailored to matching deidentified administrative data to individual-level outcome data. Probabilistic record linkage has a long tradition in economics, tracing back to the foundational framework of \citet{fellegisunter1969} and its early applications in economic history \citep{ferrie1996}. The approach has since been applied widely to link individuals across historical census records \citep{abramitzkyboustanerikkson2014, feigenbaum2016, abramitzkyetal2021, baileyetal2020} and to merge large-scale administrative datasets \citep{enamoradoetal2019}. The central challenge in my application is more severe than in most: because the H-1B administrative data is fully deidentified and contains neither names nor unique identifiers, standard text-matching approaches are infeasible. My key methodological insight is to exploit the pre-lottery employment relationship as an identifying anchor. By restricting the candidate pool to individuals observed in the Revelio data as employed at the sponsoring firm \textit{before} the lottery, I transform an otherwise intractable many-to-many matching problem---in which each application could plausibly correspond to any one of millions of users---into a tractable one, in which the candidate pool is limited to the much smaller set of individuals at the same firm. I then score candidate matches using probabilistic weights over available demographic fields \citep{enamoradoetal2019}. A well-known consequence of probabilistic linkage is that match error attenuates treatment effect estimates toward zero \citep{baileyetal2020, abramitzkyetal2021}; I address this by constructing samples of varying match quality and showing that estimated effects are generally larger in higher-confidence samples.

Finally, I study a subset of H-1B applicants who are likely to be international students with work permits through OPT. The economics literature on international students and U.S.\ labor markets establishes that F-1 enrollment is tightly linked to post-study work opportunities and that Optional Practical Training (OPT) serves as a key bridge from U.S.\ education into the skilled labor force, but it provides relatively limited evidence on downstream employer-level impacts. A first strand shows that access to U.S.\ work visas shapes both the quantity and quality of international student inflows \citep{kato_sparber_2013, shih_2016}. A second strand documents that OPT expansions increase retention and induce sorting into STEM fields and occupations, particularly among graduate students \citep{amuedo_dorantes_furtado_xu_2019, demirci_2019, amuedo_dorantes_shih_xu_2023}. Related work shows that U.S.\ higher education functions as an important pathway into the skilled labor market, with a substantial share of foreign graduates initially entering through OPT and contributing to short-run skilled labor supply \citep{bound_demirci_khanna_turner_2015, beine_bertoli_fernandes_2023}. A smaller literature examines labor-market impacts, finding heterogeneous effects across experience groups and sectors, including substitution for recent native graduates alongside complementarities with more experienced workers \citep{demirci_2020, amuedo_dorantes_furtado_2019}. However, most existing work operates at the country, field, or local labor-market level, leaving open how firms absorb OPT-driven labor supply and how these flows translate into firm outcomes. 

This paper contributes by bringing the analysis to the individual level, studying how international students use the H-1B visa and OPT in practice, and how the H-1B lottery affects their labor market outcomes. My findings suggest that for this subset of applicants, the H-1B lottery may function less as a mechanism for initial entry and more as a mechanism for retention and longer-horizon attachment. That distinction matters for how one interprets both efficiency and distributional concerns. If many applicants are already present and productive in the United States before the lottery, then the main effect of lottery loss may be to weaken firm attachment, reduce employment stability, or accelerate return migration only at the margin. At the same time, the modest average effects should not be read as evidence that the lottery is unimportant. A policy that creates substantial uncertainty, repeated reapplication costs, and employer dependence can have large welfare consequences even when average reduced-form employment responses are numerically small.


The remainder of the paper proceeds as follows. Section \ref{sec:context} describes the institutional setting, with particular attention to the H-1B lottery and the role of OPT. Section \ref{sec:data} introduces the administrative H-1B records and the Revelio outcome data, and discusses my linkage approach and sample construction. Section \ref{sec:results} lays out the empirical design and organizes the results. Section \ref{sec:conclusion} concludes.
