% !TEX root = _main.tex
\section{Background and Context: The H-1B Visa Program}

Since its inception in 1990, the H-1B visa has remained the primary pathway for temporary skilled workers to immigrate to the US. In this section, I describe key institutional background on the H-1B visa program, the lottery system used to allocate visas, and the context of the modern pre-H-1B worker and the role of Optional Practical Training (OPT).

% While the number of H-1B visas issued annually has remained capped at 85,000 for the past x years, the number of applications for H-1B visas (plotted in Figure x) has grown substantially over time. In years where demand exceeds supply (as has been the case in every year since x), USCIS conducts a lottery to allocate the limited number of visas. 

% Every year since x, the number of applications has exceeded the cap, prompting USCIS to conduct a lottery to allocate the limited number of visas, which is the source of random variation I use in this paper. 

\subsection{The H-1B Visa}
The H-1B visa is an employer-sponsored temporary work visa for workers in ``specialty occupations,'' created by the Immigration Act of 1990 as a way for firms to fill skill shortages in the US labor market \citep{uscis_h1b_specialty_2026}.

There are three key institutional details of the H-1B worker visa that are important for this paper. First, the H-1B is employer-sponsored, meaning that employers must apply for the visa on behalf of the worker, and the worker's legal status is tied to the sponsoring employer. Workers cannot self-sponsor. For employers to sponsor an H-1B worker, they must first file a Labor Condition Application (LCA) with the Department of Labor, attesting that they will pay the worker the prevailing wage for the occupation and location, and that the employment of the H-1B worker will not adversely affect the working conditions of similarly employed US workers \citep{dol_h1b_lca}.

Second, the H-1B is temporary, with a maximum duration in most cases of six years (three years of initial status plus one three-year extension) \citep{uscis_h1b_specialty_2026}.
Finally, the H-1B is dual-intent, meaning that while it does not lead directly to permanent residency, it does not preclude workers from applying for permanent residency while on H-1B status.
Many H-1B workers apply for employer-sponsored green cards under their H-1B employer, and while H-1B visas are portable across employers, pending green card applications are not, creating an incentive for workers to remain with their sponsoring employer until they receive their green card \citep{kimpei2022}.

% \textcolor{purple}{For employers to sponsor an H-1B worker, they must first file a Labor Condition Application (LCA) with the Department of Labor, attesting that they will pay the worker the prevailing wage for the occupation and location, and that the employment of the H-1B worker will not adversely affect the working conditions of similarly employed US workers. After receiving LCA certification, employers can then file Form I-129 with USCIS to petition for the H-1B visa on behalf of the worker.} Put this in 'petition' language.

\subsection{The H-1B Lottery}
H-1B employers are categorized into two groups: `cap-subject' and `cap-exempt'. Cap-exempt employers, which include non-profits and higher-education institutions, do not face restrictions on the number of H-1B visas they can sponsor. Cap-subject employers, which include most for-profit firms, are subject to an annual cap on the number of H-1B visas they can sponsor. Throughout this paper I focus on cap-subject employers, which are the relevant population for the lottery-based identification strategy.

Since 2005, the number of cap-subject H-1B visas that can be allocated in any given year has remained capped at 85,000 \citep{uscis_h1b_overview_2021}. This is partitioned into 65,000 visas for all applicants (`regular' cap) and an additional 20,000 visas reserved for applicants with an ``Advanced Degree Exemption'' (`ADE' cap), i.e. applicants with an advanced degree (Master's or higher) from a U.S. institution. In years where demand exceeds supply (as has been the case in every year since 2013), U.S. Citizenship and Immigration Services (USCIS) conducts a lottery to allocate the limited number of visas.\footnote{Technically, allocation of the H-1B visas is on a first-come, first-served basis: applications are accepted and processed on a rolling basis starting in April of each year, and once the cap is reached, no more applications are accepted. Since 2013, the cap has been reached on the first day of applications.}

Prior to 2020, firms were required to submit a full petition for each lottery applicant, including an approved LCA, an I-129 form with information about the specific worker listed on the application, and a \$10,000 processing fee. Two separate lotteries, one for ADE applicants and one for regular applicants, were then conducted among all submitted petitions, and only the petitions of lottery winners were processed.\footnote{The ADE lottery is conducted first among ADE-eligible applications. The regular lottery is subsequently conducted with all non-ADE applications \textbf{and} ADE applications not selected in the ADE lottery. ADE applications can therefore be selected through either of the ADE or non-ADE lotteries.} This meant that no information was retained on lottery losers and the cost of application was very high for employers. Once petitions of lottery winners were processed and approved, lottery winners could begin working no sooner than October of that year, six months after the lottery.\footnote{The share of rejected petitions is very small, under 5\% in most years.}

Starting in 2020, USCIS implemented an electronic registration system for the H-1B lottery \citep{uscis_h1b_registration_2020}. Under the new system, firms first submit a short electronic registration with basic information on the lottery applicant (henceforth `applicant') and a small processing fee of \$10 during a registration window in March. USCIS then conducts the random lottery separately by ADE status and notifies selected applicants (henceforth lottery `winners'). Lottery winners are then given a window of 90 days to submit a fully completed petition, including the LCA and \$10,000 processing fee \citep{uscis_h1b_fy2021_file}. There were no changes to processing of petitions or the timeline for H-1B activation after the lottery. This new registration system substantially reduced the cost of application for employers and created an electronic record of lottery applicants, including lottery losers, the crucial source of data for this paper.

% Historically, allocation of the cap-subject H-1B visas had been on a first-come, first-served basis: applications are accepted and processed on a rolling basis starting in April of each year, and once the cap is reached, U.S. Citizenship and Immigration Services (USCIS) stops accepting applications. In every year since 2013, however, the cap has been reached on the first day of the application period, prompting USCIS to conduct a lottery to allocate the limited number of visas. Firms would apply for the lottery (henceforth `applicants'), and USCIS would randomly select the number of applicants needed to fill the cap (henceforth `winners'). Once selected, winners would then have a window of time to submit a full petition for the H-1B visa, including the labor condition application and supporting documentation. If that petition is approved, the earliest start date for cap-subject employment is October 1 of the relevant fiscal year.

% Starting in FY 2020, USCIS implemented an electronic registration system for the H-1B lottery. Prior to this system, firms were required to submit the full petition at the time of application, and USCIS would conduct the lottery among all submitted petitions \textit{without retaining any information on petitioners not selected in the lottery}. 

% Under the new system, firms first submit a short electronic registration during a registration window in March. USCIS then conducts the random lottery separately by ADE status and notifies selected registrants (henceforth lottery `winners').\footnote{The ADE lottery is conducted first among ADE-eligible applications. The regular lottery is subsequently conducted with all non-ADE applications \textbf{and} ADE applications not selected in the ADE lottery. ADE applications can therefore be selected through either of the ADE or non-ADE lotteries.} 
% Lottery winners are then given a window of 90 days to submit a fully completed petition for an H-1B application, including the labor condition application and supporting documentation. If that petition is approved, the earliest start date for cap-subject employment is October 1 of the relevant fiscal year. 

% This new registration system substantially reduced the cost of application for employers (who no longer need to submit a full petition for every applicant) and created an electronic record of lottery applicants, including lottery losers, the crucial source of data for this paper. 
In reducing the cost of application, however, the new system also created scope for multiple registrations on behalf of the same beneficiary. During the years in my sample, the random selection operated at the registration level rather than at the beneficiary level, meaning that a worker with multiple registrations (through different employers) could receive more chances in the lottery.\footnote{USCIS later adopted a beneficiary-centric selection process in response to these integrity concerns, beginning after the years I study \citep{uscis_integrity_2024, uscis_beneficiary_centric_2025}.} 
Investigative reporting has documented that some employers, particularly staffing firms and outsourcing companies, have submitted large numbers of registrations on behalf of the same beneficiary through subsidiaries and shell companies, creating a lottery system that is not random at the beneficiary level \citep{Mider2024H1B}. 
I attempt to exclude these types of employers from the analysis, with further details on the data and exclusion criteria described in the data section.



\subsection{Optional Practical Training (OPT) and H-1B Lottery Applicants}

The issue at the heart of individual linkage between H-1B application data and any dataset of outcomes is that I have very limited information on lottery applicants who do not subsequently submit an H-1B petition. This issue is particularly stark if we view lottery applicants exclusively as individuals who are initially outside the United States, and work at the sponsoring employer if and only if they win the lottery. In this case, while we are able to link lottery winners more easily because we can limit our search to workers at the sponsoring employer, lottery losers are essentially impossible to link with only basic demographic data. My solution to this linkage problem will be to focus on a large and growing subset of lottery applicants \textit{who are already working for the sponsoring employer at the time of the lottery.}

The central institutional principle behind my linkage strategy is the importance of Optional Practical Training (OPT). OPT is a flexible work authorization option available to F-1 (student) visa holders, intended to provide practical training opportunities for students. The job must be related to the student's field of study, but no employer sponsor is required and self-employment is allowed. Students on F-1 (student) visas can typically work for up to 12 months after completing their studies through post-completion OPT, and eligible STEM graduates can apply for a 24-month extension, yielding up to 36 months of work authorization in total \citep{ice_practical_training_2024, uscis_opt_2024}. For many international graduates of U.S. universities, the typical sequence is therefore: graduate, begin working immediately for a U.S. employer under OPT, and then enter the H-1B lottery one or more times while already employed as a way to extend their work authorization and remain in the U.S. after their OPT expires. 

While statistics on the exact number of H-1B applicants who are initially using OPT are limited, statistics published by USCIS show that in recent years, between 50 and 70\% of H-1B petitions approved for initial employment were filed on behalf of beneficiaries already in the United States, and of those, between 70 and 80\% were filed on behalf of beneficiaries with OPT status \citep{uscis_h1b_characteristics_2024}.\footnote{Note that these numbers are not separately reported for cap-subject and cap-exempt H-1B petitions.}
I estimate in a separate data source that 94\% of F-1 visa holders who eventually transition to the H-1B visa use OPT between graduation and H-1B status.

By focusing on OPT users, I am able to restrict the relevant candidate pool for \textit{all lottery applicants} to workers already observed at the sponsoring firm prior to the lottery date. This makes the linkage problem much more tractable and by using only pre-lottery linkage variables, allows me to obtain a linked sample that is not selected on post-lottery outcomes.


% This transforms my data linkage problem from the impossible task of linking lottery applicants to ``everyone in the world with similar demographics'' to the more feasible task of linking lottery applicants to ``workers already observed at the sponsoring firm around the lottery date.''

% This has three consequences for the analysis. First, many lottery applicants are already attached to the sponsoring employer before the lottery takes place. That creates a feasible linkage design, because the relevant candidate pool in LinkedIn data is not ``everyone in the world with similar demographics'' but rather ``workers already observed at the sponsoring firm around the lottery date.'' Second, lottery loss need not imply immediate separation from the employer or immediate exit from the United States. A worker who loses can remain under the initial 12-month OPT period, under the STEM extension, through cap-gap protection if a later petition is pending, or through another temporary status \citep{uscis_cap_gap_2025}. Third, the treatment effect of winning should vary with remaining runway on OPT. The difference between winning and losing is likely to be largest when alternative work authorization is about to expire.

% Unlike many other visa pathways, the H-1B visa operates using a lottery system. 

% (Not important for this paper: information on employer timeline, LCA, etc.)
% Employer timeline -- useful for further proof that employers are unlikely to hire an OPT eligible person directly via H1B?

% \subsection{Eligibility}
% - can apply from inside or outside the country
% - employer must certify...

% \subsection{Terms/Benefits (what you get)}
% - pathway to greencard

% \subsection{Lottery Details}
% - ADE
% - online vs not (no data on losers before fy2019)
% - if you win, submit i129

% \subsection{OPT}

% %\section{Institutional Context}
% %\label{sec:context}

% \subsection{The H-1B program}

% The H-1B is a temporary employment-based visa for workers in specialty occupations. In broad terms, the employer must show that the job requires specialized knowledge and that the worker has at least the relevant bachelor's-level training, while the petitioning firm files on the worker's behalf \citep{uscis_h1b_specialty_2026}. Cap-subject H-1B status is typically granted for an initial period of up to three years and can generally be extended to a maximum of six years, with some exceptions related to permanent-residency processing \citep{uscis_h1b_specialty_2026}. The key feature for this paper is that H-1B status is tied to an employer-worker relationship. A worker cannot self-petition into the cap-subject H-1B category, and although H-1B workers can later move across employers, doing so requires another employer to file on their behalf. In practice, this linkage between legal status and the sponsoring employer can create employer stickiness, especially when the worker is also navigating permanent-residency sponsorship \citep{kimpei2022}.

% Congress has fixed the annual cap for new cap-subject H-1B visas at 65{,}000 for the regular cap plus 20{,}000 visas reserved for workers eligible for the advanced-degree exemption (ADE), sometimes called the master's cap \citep{uscis_h1b_overview_2021}. Eligibility for the ADE requires a qualifying U.S. advanced degree. When demand exceeds supply, USCIS allocates visa slots by lottery. During the period studied here, demand exceeded the cap by a wide margin, making random selection the relevant source of identifying variation in most years.

% \subsection{Lottery timing and why selection is not the same as visa issuance}

% The timing of the cap-subject H-1B process matters for both identification and interpretation. Since the introduction of electronic registration for the FY2021 cap season, employers first submit a short electronic registration during a registration window in March \citep{uscis_h1b_registration_2020}. USCIS then conducts the random selection process and notifies selected registrants. Petitioners with selected registrations have a filing window of at least 90 days to submit the full Form I-129 petition, including the labor condition application and supporting documentation \citep{uscis_h1b_fy2021_file, uscis_h1b_registration_process_2026}. If that petition is approved, the earliest start date for cap-subject employment is October~1 of the relevant fiscal year \citep{uscis_h1b_fy2021_file}. Appendix Figure \ref{fig:h1b_timeline} summarizes the timeline.

% Two implications follow. First, lottery selection is not the same as final H-1B take-up. A selected registration must still be converted into a filed petition and then adjudicated. Second, the relevant horizon between lottery resolution and H-1B activation is long. Employers commonly learn the lottery outcome in late March, but the new H-1B status generally does not begin until October. For workers already employed under another temporary status, that gap can often be bridged. For workers with no alternative work authorization, however, the lottery outcome can be pivotal.

% A second institutional detail is the treatment of advanced-degree-exempt applicants. Under the rules in force for the period I study, the order of selection was the regular cap first and the advanced-degree exemption second, increasing the probability that U.S. advanced-degree holders receive a visa relative to otherwise similar applicants \citep{uscis_h1b_final_rule_2019, uscis_h1b_overview_2021}. That feature is central for the empirical design because the lottery is random only conditional on the applicant's lottery bucket. Throughout the paper I therefore condition on, or interact treatment with, ADE status.

% \subsection{OPT and the modern pre-H-1B worker}

% The central institutional fact behind the linkage strategy is the importance of Optional Practical Training (OPT). F-1 students can typically work for up to 12 months after completing their studies through post-completion OPT, and eligible STEM graduates can apply for a 24-month extension, yielding up to 36 months of work authorization in total \citep{ice_practical_training_2024, uscis_opt_2024}. For many international graduates of U.S. universities, the typical sequence is therefore: graduate, begin working immediately for a U.S. employer under OPT, and then enter the H-1B lottery one or more times while already employed.

% This has three consequences for the analysis. First, many lottery applicants are already attached to the sponsoring employer before the lottery takes place. That creates a feasible linkage design, because the relevant candidate pool in LinkedIn data is not ``everyone in the world with similar demographics'' but rather ``workers already observed at the sponsoring firm around the lottery date.'' Second, lottery loss need not imply immediate separation from the employer or immediate exit from the United States. A worker who loses can remain under the initial 12-month OPT period, under the STEM extension, through cap-gap protection if a later petition is pending, or through another temporary status \citep{uscis_cap_gap_2025}. Third, the treatment effect of winning should vary with remaining runway on OPT. The difference between winning and losing is likely to be largest when alternative work authorization is about to expire.

% \subsection{Multiple registrations and integrity concerns}

% The move to electronic registration substantially lowered the cost of entering the lottery. That change reduced paperwork for legitimate employers, but it also created scope for multiple registrations on behalf of the same beneficiary. During the years in my sample, the random selection operated at the registration level rather than at the beneficiary level, meaning that a worker with multiple registrations could receive more chances in the lottery. USCIS later adopted a beneficiary-centric selection process in response to these integrity concerns, beginning after the main years I study \citep{uscis_integrity_2024, uscis_beneficiary_centric_2025}. This matters empirically because duplicate-heavy employers and outsourcing-style applications can distort both the interpretation of the lottery and the quality of individual linkage. I therefore describe the multiple-registration issue explicitly in the data section and treat it as both an institutional feature of the sample period and a source of robustness checks in the linked analysis.
