% !TEX root = _main.tex
\section{Results}
\label{sec:results}

\subsection{Empirical specification}

The main specification compares lottery-selected and non-selected applicants in the linked sample, conditioning on advanced-degree-exempt status because ADE applicants face a different lottery assignment process. For applicant $i$ in lottery year $t$ at firm $c$, I estimate:
\begin{equation}
\label{eq:mainreg}
 y_{ict}^s = \beta_0 + \beta_1 Win_{ict} + \beta_2 ADE_{it} + \gamma_{ct} + \varepsilon_{ict}^s,
\end{equation}
where $y_{ict}^s$ indicates the outcome of interest measured $s$ years after the lottery year $t$, $Win_{ict}$ indicates lottery selection for applicant $i$ in year $t$ with firm $c$, $ADE_{it}$ indicates eligibility for the advanced-degree exemption, and $\gamma_{ct}$ denotes firm-by-lottery-year fixed effects. Outcomes are aggregated to the applicant level using the probabilistic match weights described in Section~\ref{sec:linkage}, and standard errors are clustered at the firm level. The parameter $\beta_1$ captures the effect of winning the H-1B visa lottery on outcome $y_{ict}$. The key identifying assumption is that, conditional on ADE status and firm-lottery-year cells, lottery selection is as good as random and does not differentially affect the probability of appearing in the matched sample. The fixed effects control for any time-varying firm-level factors that could confound the relationship between lottery selection and outcomes.

My main outcomes of interest relate to individual location, employer switching, `promotions', and education enrollment. For location, I measure whether the worker is observed in the United States or in their country of origin two years post-lottery. For employer switching, I measure whether the worker has an active position at the same firm or a different firm than the sponsoring firm two years post-lottery. For promotions, I measure whether the worker has started a new position at the same firm after the lottery, among applicants who subsequently remained at the same firm after the lottery. For education, I measure whether the worker has an active education spell started after the lottery. These outcomes capture key dimensions of labor market attachment and mobility that may be affected by lottery selection.
% Table~\ref{tab:balance} documents pre-lottery covariate balance by winner status within ADE groups. For ADE applicants, gender shows no significant imbalance ($p = 0.108$), while age and years since graduation are slightly lower among winners, likely reflecting mechanical sample composition from lottery stratification. For regular-cap applicants, winners are more likely to be at high-reputation employers, consistent with higher application rates at such firms rather than differential lottery outcomes. Overall, the balance is broadly consistent with quasi-random assignment conditional on ADE status and firm-lottery-year cells.

% \begin{table}[htbp]
% \centering
% \caption{Pre-Lottery Covariate Balance by Winner Status}
% \label{tab:balance}
% \footnotesize
% \begin{tabular}{lrrrrrr}
% \toprule
% & \multicolumn{3}{c}{ADE = 0} & \multicolumn{3}{c}{ADE = 1} \\
% \cmidrule(lr){2-4}\cmidrule(lr){5-7}
% Variable & Loser & Winner & p-val & Loser & Winner & p-val \\
% \midrule
% Age at lottery                    & 30.946 & 30.291 & 0.000*** & 30.954 & 30.265 & 0.000*** \\
% Advanced degree eligible          & 0.419  & 0.497  & 0.000*** & \multicolumn{3}{c}{(full sample)} \\
% Years since graduation            & 1.950  & 1.740  & 0.000*** & 2.021  & 1.824  & 0.000*** \\
% Female                            & 0.385  & 0.402  & 0.000*** & 0.416  & 0.423  & 0.108    \\
% \# applications (multiplicity)    & 3.336  & 3.360  & 0.250    & 3.377  & 3.198  & 0.000*** \\
% \# unique countries (match)       & 2.029  & 2.013  & 0.154    & 1.902  & 1.813  & 0.000*** \\
% High-reputation employer          & 0.307  & 0.344  & 0.000*** & 0.338  & 0.375  & 0.000*** \\
% \midrule
% $N$ (ADE=0: losers / winners)     & 38,502 & 22,480 & & & & \\
% $N$ (ADE=1: losers / winners)     & & & & 27,810 & 22,230 & \\
% \bottomrule
% \end{tabular}
% \begin{tablenotes}
% \item \textit{Notes}: Sample is the U.S.-educated linked sample (N = 111,022). Loser and Winner columns report means of pre-lottery covariates; p-val is from a two-sample $t$-test. ADE = Advanced Degree Exempt. \sym{*} $p<0.10$, \sym{**} $p<0.05$, \sym{***} $p<0.01$.
% \end{tablenotes}
% \end{table}

\subsection{Main results}

Table~\ref{tab:main_results} presents the main regression estimates for six outcomes measured two years after the lottery, using the U.S.-educated linked sample (N = 70,471).\footnote{Of 111,022 applications in the U.S.-educated linked sample, 40,551 are singletons---the only application in their firm-year cell---and are dropped because firm-year fixed effects are not identified for them.} All regressions include firm-by-lottery-year fixed effects; standard errors are clustered by firm.

The point estimates for lottery winners are positive and statistically significant across several key outcomes. Winning the lottery raises the probability of being observed in the United States two years post-lottery by 0.53 percentage points (0.6\%\sym{***}) and reduces the probability of appearing in one's home country by 0.14 percentage points (6.4\%\sym{**}). On the employment margin, winners are 0.44 percentage points more likely to remain at the sponsoring firm (0.8\%\sym{**}) and equally less likely to hold a new position at a different employer (1.0\%\sym{**}), consistent with the visa reducing employer mobility. Winners are also marginally more likely to have enrolled in new education post-lottery (1.2\%\sym{*}). By contrast, the conditional probability of a new within-firm position---among applicants who remain at the same firm---shows no significant winner effect (0.1\%, N = 8,350).

\begin{table}[htbp]
\centering
\caption{Main Effects of H-1B Lottery Selection: Two Years Post-Lottery}
\label{tab:main_results}
\footnotesize
\input{/home/yk0581/output/reg/tables/paper_main_results.tex}
\begin{tablenotes}
\item \textit{Notes}: OLS estimates. Sample: U.S.-educated linked sample (N = 70,471). All outcomes measured two years post-lottery. \textit{In U.S.} = observed in the United States (from position or education location field). \textit{In home ctry} = observed in country of origin. \textit{Same firm} = indicator for active position at sponsoring firm. \textit{New pos.\ (cond.)} = new post-lottery position at same firm, estimated on the subsample with \textit{Same firm} = 1 (N = 8,350). \textit{New diff.\ firm} = active position at a different firm started after lottery. \textit{New educ.} = active education spell started after lottery. All regressions include firm-by-lottery-year fixed effects. Standard errors (in parentheses) clustered by firm. \sym{*} $p<0.10$, \sym{**} $p<0.05$, \sym{***} $p<0.01$.
\end{tablenotes}
\end{table}

% \subsection{Remaining in the United States}

% Columns (1) and (2) of Table~\ref{tab:main_results} capture the geographic margin of the lottery. Winners are 0.53 percentage points more likely to be observed in the United States two years post-lottery ($p < 0.01$) and 0.14 percentage points less likely to be observed in their home country ($p < 0.05$). Together, these effects indicate that winning the visa lottery meaningfully stabilizes U.S. geographic attachment: losers are both less likely to remain in the United States and more likely to return home.

% That the effects are not larger is consistent with a substantial share of lottery losers finding alternative pathways to remain in the United States, most plausibly through continued OPT, STEM-OPT extensions, cap-exempt employer arrangements, or repeat lottery participation in subsequent years. The pre-filtered and strict-threshold samples in Table~\ref{tab:robustness} yield larger and more precisely estimated effects, consistent with attenuation from measurement error in the baseline.

% \subsection{Career adjustment: firm switching, promotion, and education}

% Columns (3), (5), and (6) of Table~\ref{tab:main_results} speak to the career adjustment margins. Winning the lottery increases two-year retention at the sponsoring firm by 0.44 percentage points ($p < 0.05$) and reduces new employment at a different firm by an equal and opposite amount ($p < 0.05$). This symmetric pattern implies that the visa constrains employer mobility: winners are locked into the sponsoring firm, while losers who remain in the United States are more likely to switch employers. New education enrollment is modestly higher among winners ($+$0.42 pp, $p < 0.10$), though the magnitude is small. Among those who remain at the sponsoring firm, however, there is no significant effect on the probability of starting a new within-firm position (column 4), suggesting the visa does not accelerate within-firm career progression.

\subsection{Robustness to linkage quality and sample selection}

Table~\ref{tab:robustness} reports the winner coefficient for all six outcomes across five sample variants: the U.S.-educated baseline, the one-to-one sample (optimal bipartite matching that assigns each applicant to at most one Revelio candidate), the pre-filtered sample (excluding applicants from countries with high candidate multiplicity), and three strict-threshold samples that progressively restrict to higher-quality matches (Q25, Q50, and Q75 score thresholds). The key pattern is that winner effects are generally larger in higher-confidence samples, consistent with attenuation from match error in noisier baseline cells.

In the pre-filtered sample (N = 10,425), winning increases two-year firm retention by 2.8 percentage points ($p < 0.01$) and reduces new employer switching by an equal amount ($p < 0.01$); the U.S.-presence effect is 1.0 percentage point ($p < 0.05$). In the strictest sample (Q75, N = 15,218), the U.S.-presence effect reaches 2.0 percentage points ($p < 0.01$), retention rises by 2.1 percentage points ($p < 0.05$), and the conditional within-firm new position effect becomes negative and significant ($-$3.0 pp, $p < 0.05$). These results support the interpretation that the baseline estimates, while already significant, are attenuated by measurement error and understate the true lottery effects for well-matched applicants.

The internal validity of the research design requires that lottery selection not differentially affect the probability of appearing in the matched sample. The external validity caveat is explicit: the paper speaks to U.S.-educated H-1B applicants already employed at sponsoring firms and visible in LinkedIn-based data before the lottery, rather than to all H-1B applicants worldwide.

\begin{table}[htbp]
\centering
\caption{Robustness: Winner Effects Across Sample Variants}
\label{tab:robustness}
\footnotesize
\input{/home/yk0581/output/reg/tables/paper_robustness.tex}
\begin{tablenotes}
\item \textit{Notes}: Each cell reports the OLS estimate of $\hat\beta_1$ (winner effect) from equation~\eqref{eq:mainreg} with standard errors clustered by firm in parentheses. All regressions include firm-by-lottery-year fixed effects. Outcomes measured two years post-lottery; see Table~\ref{tab:main_results} for definitions. One-to-one uses optimal bipartite matching (Jonker--Volgenant) to assign each applicant to at most one Revelio candidate. Pre-filtered excludes applicants from countries with high candidate multiplicity (Southern Asia, East Asia, UK, Canada, Australia). Strict (Q25/Q50/Q75) restricts to applicants whose match quality score exceeds the 25th, 50th, or 75th percentile threshold, respectively. \sym{*} $p<0.10$, \sym{**} $p<0.05$, \sym{***} $p<0.01$.
\end{tablenotes}
\end{table}



\subsection{Heterogeneity and Mechanisms}

A particularly important heterogeneity dimension is the amount of time the worker appears to have remaining before OPT exhaustion. The code constructs a measure of time since graduation, which is a natural proxy for remaining OPT runway. The prediction is straightforward: effects of winning should be larger for workers who are closer to the end of their allowable OPT period. If the treatment effect grows when alternative authorization is scarce, that is exactly what the institutional context predicts.

Table~\ref{tab:het_same_firm} presents heterogeneous effects on two-year U.S.\ retention (\textit{In U.S.}) across two dimensions: years since graduation at the time of the lottery (columns 1--4) and employer reputation class (columns 5--6). The graduation-year subgroups partition applicants by $\Delta g$, defined as lottery year minus one minus last graduation year; $\Delta g = 0$ and $\Delta g = 1$ correspond to workers still within their initial two-year OPT window, while $\Delta g \geq 2$ covers those on STEM-OPT extensions or other bridging arrangements. The reputation subgroups split by whether the sponsoring firm has no recorded reputation score (\textit{norep}) or a high reputation score (\textit{highrep}).

\begin{table}[htbp]
\centering
\caption{Heterogeneous Effects on Two-Year U.S.\ Retention by Years Since Graduation and Employer Reputation}
\label{tab:het_same_firm}
\footnotesize
\input{/home/yk0581/output/reg/tables/paper_het_in_us2.tex}
\begin{tablenotes}
\item \textit{Notes}: OLS estimates of $\hat\beta_1$ (winner effect) from equation~\eqref{eq:mainreg}. Outcome: \textit{In U.S.} (active U.S.\ position two years post-lottery). Each panel corresponds to a sample variant; see Table~\ref{tab:robustness} for definitions. One-to-one uses optimal bipartite matching to assign each applicant to at most one Revelio candidate. Strict (Q75) restricts to applicants whose match quality score exceeds the 75th percentile threshold. Within each panel, columns (1)--(4) restrict to applicants with $\Delta g$ equal to the indicated value (rounded), where $\Delta g = $ lottery year $-$ 1 $-$ last graduation year; columns (5)--(6) restrict to applicants at no-reputation and high-reputation employers, respectively. All regressions include firm-by-lottery-year fixed effects. Standard errors (in parentheses) clustered by firm. \sym{*} $p<0.10$, \sym{**} $p<0.05$, \sym{***} $p<0.01$.
\end{tablenotes}
\end{table}

\subsection{Interpreting the magnitudes}

The central finding is that winning the H-1B lottery significantly increases U.S. presence and retention at the sponsoring firm while reducing new employer mobility. Two features of the results merit emphasis.

First, the baseline effects are likely attenuated by probabilistic linkage error. Even if the true individual-level effect is larger, mixing correct and incorrect candidate links in the weighted average compresses estimates toward zero. The generally larger estimated effects in higher-confidence samples---ranging from 0.53 pp (In U.S.) in the baseline to 2.0 pp in the Q75 strict sample---is consistent with this interpretation. The pre-filtered winner effect on two-year U.S.\ retention (2.8 pp) is more than six times the baseline point estimate (0.44 pp), suggesting the baseline substantially understates the true effect.

Second, even the baseline effects are economically meaningful for a subpopulation of U.S.-educated workers whose visa status is genuinely at stake. Among U.S.-trained workers already employed under OPT, losing the lottery raises separation risk and the probability of leaving the United States, but many losers find ways to remain through STEM-OPT extensions, cap-exempt employment, or repeat lottery applications. The H-1B is thus best characterized as a \textit{stability lottery} rather than an entry lottery for this subgroup: winning reduces the risk of disruption and locks workers into the sponsoring firm, but does not transform a worker who would otherwise leave into one who stays. The largest effects appear for applicants with limited alternative pathways---those visible in higher-quality linked samples---for whom the lottery outcome is more binding.
