\clearpage
\section{Linking H-1B Applications to Revelio Profiles}
\label{sec:appendix_linkage}

This appendix gives a self-contained description of the linkage used to connect deidentified H-1B lottery applications to LinkedIn-based worker histories from Revelio. The central difficulty is that the administrative H-1B records contain no names or personal identifiers for the full applicant pool. A global search over all Revelio users would therefore be too noisy to be useful. The linkage becomes feasible because many recent cap-subject applicants are already working for the sponsoring employer when they enter the lottery, often under Optional Practical Training (OPT). I use that pre-lottery employment relationship as the anchor for the match.

The linkage proceeds in three steps. First, I align employers across the two datasets. Second, I construct on the Revelio side the limited set of demographic and education variables that can be compared to the administrative records. Third, within each sponsoring employer-year cell, I rank plausible worker profiles and carry the resulting match uncertainty forward into the analysis through applicant-level match weights rather than forcing a deterministic one-to-one match.

\subsection{A. Employer crosswalk and in-scope employer-years}

The first stage creates a crosswalk between employers in the H-1B files and employers in Revelio. This stage uses cleaned employer names, employer tax identifiers where available, location and industry information, and a stock of previously validated firm links. Straightforward cases are kept directly. Ambiguous cases are narrowed using fuzzy comparison rules and then reviewed with a large language model that determines whether a candidate Revelio company corresponds to the same economic employer. The model is used only for firm identity resolution, such as rebrandings, spelling variants, and subsidiary relationships; it is not used to identify individual workers.

The employer crosswalk is intentionally many-to-many at the employer-year level. A single economic employer can appear under more than one vendor-specific company identifier in Revelio, and collapsing those identifiers too early would create false non-matches downstream. The pipeline therefore carries forward all valid employer-year links and later uses workers' own position histories to give more weight to the most credible employer mapping.

Before any person-level matching takes place, the code also defines a conservative employer-year sample. The current working sample keeps only employer-year cells with no duplicate registrations and at most ten H-1B applications. This restriction removes the highest-multiplicity cells, where individual matching is least reliable and where outsourcing-style employers generate especially diffuse candidate pools.

\subsection{B. Preparing Revelio profiles for matching}

The Revelio side is pre-processed to focus on workers who could plausibly belong to the recent H-1B applicant pool. The cleaned profile file keeps users with U.S.-based positions at employers in the linked employer sample and uses position histories beginning in 2015 or later. Open-ended jobs are cleaned conservatively, and positions are collapsed to the employer level around the lottery date.

The pipeline also removes likely duplicate profiles. A pair of profiles is treated as a duplicate only when the profiles share a normalized name and the same employer, and when at least one additional overlap condition is satisfied: overlapping job dates, overlapping education dates, or a common school. Within such duplicate sets, the profile with the richer work history is retained. This is designed to avoid collapsing genuinely different workers who happen to share a common name at a large employer.

Finally, the Revelio cleaning stage excludes profiles with clear evidence of U.S. secondary schooling, which are less likely to belong to the foreign-born population of interest. It also records whether the profile shows U.S. postsecondary education and whether the worker appears to qualify for the advanced-degree exemption. The paper's preferred linked sample later requires confirmed U.S. postsecondary education, but that restriction is imposed after the broader cleaned profile file is built.

\subsection{C. Variables inferred on the Revelio side}

Because the H-1B data are deidentified, the person-level match relies on a small set of fields that are either observed or inferable in both sources.

\paragraph{Country of origin.}
Country evidence is built from several sources. School histories identify the country of attended institutions. Name-based models provide both country-level and broader regional predictions. Position histories provide an additional check when a user's observed work history lines up with the same origin country. The pipeline combines these inputs into a country-level signal and a broader regional signal, while separately flagging cases in which the country prediction is unusually uncertain.

\paragraph{Year of birth.}
Estimated year of birth is inferred from education timing. When a high school record is available, the birth-year estimate comes from the implied age at high school completion. Otherwise it is backed out from postsecondary start and end dates, with adjustments for degree type.

\paragraph{Sex.}
The administrative records contain sex, while Revelio does not. The code therefore constructs a name-based sex probability using more than one name model and treats this as a noisy comparison field rather than a deterministic identifier.

\paragraph{Education and occupation.}
Education histories are also used to identify U.S. postsecondary attendance, advanced-degree status, the year of the most recent U.S. graduation, and broad field of study. Position titles are cleaned and mapped to H-1B-relevant occupation rankings. These fields are useful both for sharpening the match and for defining heterogeneity in the later analysis.

\subsection{D. Building applicant-specific candidate pools}

For each H-1B application, the candidate pool is defined inside the linked employer-year cell. In the current implementation, the first pass is deliberately broader than exact country matching: applicants are initially paired with Revelio users at the same employer who fall in the same broad region of origin. Exact country agreement then receives much more weight at the ranking stage. This design allows the pipeline to retain plausible cases when country classification is noisy without treating broad regional agreement as equivalent to a true country match.

Timing restrictions are central. A candidate must appear to have started at the sponsoring employer within the few years before the lottery and still be employed there at the March filing date associated with that lottery. In the code, the reference date is March 1 of the calendar year preceding the fiscal-year label in the H-1B data. Candidates are also screened using age and education timing so that the implied life cycle is consistent with a recent student-to-work transition rather than with a much older worker. Profiles that clearly look unrelated to the skilled H-1B applicant pool are removed as well.

These restrictions reflect the economics of the modern H-1B system. For many recent applicants, the relevant comparison is not between a worker outside the United States and a worker already employed at the sponsor, but between lottery winners and lottery losers who are both already working for that employer before the visa decision is realized. That institutional fact is what makes the person-level linkage tractable.

\subsection{E. Ranking candidates and carrying forward uncertainty}

After the candidate pool is defined, each applicant-candidate pair receives a composite score. Country-of-origin agreement is the dominant component of the score. Consistency in sex and year of birth provides secondary information. Occupation provides an additional refinement but does not drive the match on its own. Candidate scores are also adjusted for employer-link quality: a candidate receives more credit when the candidate's own position history directly supports the sponsoring employer match and less credit when the employer crosswalk itself is weak.

The score is then normalized within applicant to form match weights that sum to one across retained candidates. Those weights are the object carried into the regression analysis. This is important conceptually. A deterministic one-to-one match would hide uncertainty and make a single mistaken assignment disproportionately influential. By contrast, the weighted approach preserves ambiguity transparently and turns linkage noise mainly into attenuation rather than into arbitrary reclassification.

The code records several diagnostics that are used later in the paper: the number of retained candidates per applicant, the top candidate's weight, the gap between the top two candidates, and indicators for ambiguous cases in which the top candidate is only weakly separated from the runner-up.

\begin{table}[H]
\centering
\caption{How the current scoring rules are used}
\label{tab:link_params}
\begin{tabularx}{\textwidth}{@{}l X@{}}
\toprule
Component & Role in the linkage \\
\midrule
Country of origin & Main identifying signal. Exact country agreement matters most, while broader regional agreement is used only as a fallback when country evidence is weak or noisy. \\
Sex and year of birth & Secondary signals that down-rank otherwise plausible candidates when the profile does not fit the administrative record. \\
Employer-link quality & Candidate scores are discounted when the employer crosswalk is weak and receive full credit when the candidate's own job history clearly supports the sponsoring employer match. \\
Occupation and field & Low-weight refinements that help favor profiles consistent with skilled H-1B-type work. \\
Ambiguity flag & Applications are flagged when the leading candidate is not clearly separated from the runner-up. \\
Strict sample & Keeps only dominant top-ranked matches with strong absolute score, strong employer-link evidence, strong country evidence, and a usable birth-year estimate. \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{F. Linked analysis samples}

The pipeline produces several linked samples for analysis.

\begin{itemize}
    \item \textbf{Broad linked sample.} Keeps all retained candidates after the main plausibility filters.
    \item \textbf{Preferred U.S.-educated sample.} Further requires the matched Revelio profile to show U.S. postsecondary education. This is the paper's preferred sample because it most closely targets workers likely to have entered the sponsoring firm through OPT.
    \item \textbf{Multiplicity-capped samples.} Restrict attention to applications with only a small number of retained candidates, which reduces attenuation from diffuse match weights.
    \item \textbf{Pre-filtered sample.} Excludes origin-country groups that generate especially large candidate pools in Revelio, mainly because both H-1B application counts and online-profile coverage are extremely high.
    \item \textbf{Strict sample.} Keeps only the top-ranked candidate when that candidate dominates the applicant's weight, clears a high absolute score threshold, has strong employer-link evidence, and has strong country evidence.
\end{itemize}

These variants are useful for a simple reason: if linkage error mainly attenuates treatment effects, estimates should generally become larger in higher-precision samples even as the sample size falls.

\subsection{G. Outcomes constructed from linked profiles}

Once workers are linked, I construct outcomes from Revelio position and education histories and aggregate them to the applicant level using the match weights. The retention outcome is defined at the employer level rather than the job-title level, which makes it less sensitive to noisy title coding and internal reorganizations. Likewise, the geographic outcomes are based on observed location fields, so they should be interpreted as evidence on observed geographic attachment rather than as direct measures of legal status.

\begin{table}[H]
\centering
\caption{Outcome concepts used after the linkage}
\label{tab:outcome_defs}
\begin{tabularx}{\textwidth}{@{}l X@{}}
\toprule
Outcome & Construction in words \\
\midrule
Still at sponsoring firm & Whether the linked worker is observed in an active job at the sponsoring employer one, two, or three years after the lottery. \\
Move to a different employer & Whether the worker starts a post-lottery job at a different employer. \\
Internal move or promotion & Whether the worker starts a new post-lottery position at the same employer. \\
Observed in the United States & Whether any job or education record places the worker in the United States in the relevant post-lottery year. \\
Observed in origin country & Whether any job or education record places the worker in the worker's country of origin in the relevant post-lottery year. \\
New education & Whether the worker begins a new education spell after the lottery. \\
Compensation & An annual compensation measure built from Revelio's imputed pay fields and the share of the year covered by each active job. \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{H. Validation}

The main ex-post validation exercise uses lottery winners, for whom the administrative files contain much richer petition information than for lottery losers. For those cases, I compare the linked Revelio profiles to the administrative records on education level, advanced-degree institution when relevant, field of study, and job title. Match quality rises strongly with the linkage weight and is highest in the strict sample, which supports the interpretation of the weights as meaningful measures of matching confidence rather than arbitrary scaling factors.

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    node distance=0.85cm,
    box/.style={draw, rounded corners, align=left, fill=gray!8, minimum height=1.0cm, text width=0.82\textwidth, inner sep=6pt},
    arr/.style={-{Latex[length=2.5mm]}, thick}
]
\node[box] (a) {\textbf{H-1B applicant records}\\Deidentified applicant-level files with lottery outcome, sponsoring employer, and basic demographics.};
\node[box, below=of a] (b) {\textbf{Employer crosswalk}\\Deterministic and fuzzy employer matching, with large-language-model review of ambiguous firm identities.};
\node[box, below=of b] (c) {\textbf{Revelio cleaning and inference}\\Clean job and school histories, remove likely duplicate profiles, and infer origin, sex, birth year, education, and occupation-related signals.};
\node[box, below=of c] (d) {\textbf{Applicant-specific candidate pools}\\Search only within the linked employer-year cell and retain workers whose timing and profile histories make pre-lottery employment plausible.};
\node[box, below=of d] (e) {\textbf{Probabilistic ranking}\\Score candidate workers, normalize scores to applicant-level weights, and flag ambiguous matches.};
\node[box, below=of e] (f) {\textbf{Weighted outcomes}\\Construct worker outcomes from career and education histories and aggregate them to the applicant level using the match weights.};

\draw[arr] (a) -- (b);
\draw[arr] (b) -- (c);
\draw[arr] (c) -- (d);
\draw[arr] (d) -- (e);
\draw[arr] (e) -- (f);
\end{tikzpicture}
\caption{Linkage pipeline from deidentified H-1B records to applicant-level outcomes}
\label{fig:link_pipeline}
\end{figure}
